---
title: "1.assignment"
author: "Subhash.M"
date: "2025-02-09"
output:
bibliography: /work/jyanglab/subhash/0.assignment_agro_932/o.asssignment_agro_932/profiling/ref.bib
---

# Assignment-1

## data download and methods described for the selection scan


The plant species I am working and used for this assignment is sorghum *sorghum bicolar* I am using the data published on the sorgsd database from the publication
[@zhang2018sweet] [@liu2021sorgsd].Sorghum is the 5th most cultivated cereal with a genome size of **720 Mb**\


I have downloaded 10 samples of wild population *(n = 10)* and 10 samples of improved sorghum data *(n = 10)*. from the [@zhang2018sweet] paper. I have used the following code to download the data from genome sequence archive under accession number **CRA00061**.

In this study they have used 241 sorghum accessions (42 are wild sorghum) for studying the dry gene which is responsible for encoding NAC transcription factor and controls pitchy/juicy stem trait. mutation in these dry gene lead to the origin of sweet sorghum.

### paths for the data

**wildtype data** = "/work/jyanglab/subhash/0.assignment_agro_932/1.wild_sorghum/" \

**Improved data** = "/work/jyanglab/subhash/0.assignment_agro_932/2.improved_sorghum/" \ 

**Rference genome** (version5) = "/work/jyanglab/subhash/0.assignment_agro_932/0..refrence/Phytozome/PhytozomeV13/" \

```{r setup}
#I have set the path to this directory, this makes someone to run the code very easily
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('/work/jyanglab/subhash/0.assignment_agro_932/o.asssignment_agro_932')) 
```
[@zhang2018sweet]have conducted whole genome resequencing generated a total of 7.39 GB paired end reads of 150bp in length, 1.11 Tb of bases in total.
all the 241 sorghum lines sequences using Illumina HiSeq X ten platform and used paired end sequencing. The average sequecning depth of all the sorghum accessions used were \~ 5-6.7 X. They called the SNPs using GATK (Genome Analysis ToolKit) after aligned with the reference genome of BTx623 (v3.1) with BWA -mem algorithm. They identified \~32 million SNPs and 4.2 million InDels from the 241 lines of sorghum.

# selection scan method used in the publication

For the selection scan they have used XPCLR software to calculate the XP-CLR score between the sub-groups with non-overlapping window size of 10 Kb. They also filtered the SNPs with the missing rate of 0.5 and minimum depth of 2 and minimum genotype quality 5, the average genetic distance for each chromosome was estimated from previous studies.

They also conducted additional population genetic studies the nucleotide diversity (pi,π) and Tajima's D using VCFtools SNPs used to calculate Tajima's D in the wild and pithy population was 37 and 30 respectively. for all these analysis the S. propinquum is used as the ancestor.

```{r,  eval=FALSE}
#firstly, I have followed the data dir system to organize my data and code fro higher producbility.
#always follow dir system

 install.packages('ProjectTemplate')
 library('ProjectTemplate')
 create.project('letters')
```

# data downoad for the 10 wildtype samples

```{bash, eval=FALSE}

#I have downloaded n=10 wild sorghum genotype data

cd /work/jyanglab/subhash/0.assignment_agro_932/1.wild_sorghum/

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023308/CRR023308_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023308/CRR023308_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023319/CRR023319_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023319/CRR023319_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023320/CRR023320_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023320/CRR023320_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023321/CRR023321_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023321/CRR023321_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023322/CRR023322_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023322/CRR023322_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023325/CRR023325_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023325/CRR023325_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023326/CRR023326_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023326/CRR023326_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023327/CRR023327_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023327/CRR023327_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023396/CRR023396_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023396/CRR023396_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023397/CRR023397_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023397/CRR023397_r2.fq.gz

```

# data sownload for the 10 improved samples

```{bash, eval=FALSE}
cd /work/jyanglab/subhash/0.assignment_agro_932/2.improved_sorghum/

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023272/CRR023272_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023272/CRR023272_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023293/CRR023293_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023293/CRR023293_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023294/CRR023294_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023294/CRR023294_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023233/CRR023233_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023233/CRR023233_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023260/CRR023260_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023260/CRR023260_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023271/CRR023271_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023271/CRR023271_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023289/CRR023289_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023289/CRR023289_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023274/CRR023274_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023274/CRR023274_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023280/CRR023280_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023280/CRR023280_r2.fq.gz

wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023281/CRR023281_f1.fq.gz
wget ftp://download.big.ac.cn/gsa3/CRA000611/CRR023281/CRR023281_r2.fq.gz
```

# Refrences